---
title: "Week5 R Assignment"
output: html_document
---

5 Matrices

```{r}
A <- matrix(c(1,-1,-1,-1),nrow=2,ncol=2)
B <- matrix(c(2,-1,3,-2),nrow=2,ncol=2)
C <- matrix(c(1,0,0,0),nrow=2,ncol=2)
D <- matrix(c(0,1,0,1,0,0,0,0,1),nrow=3,ncol=3)
E <- matrix(c(1,0,0,0,0,1,0,1,0),nrow=3,ncol=3)
```

Idempotent Matrices

Only C is idempotent

```{r}
A %*% A
B %*% B
C %*% C 
D %*% D
E %*% E
```

Orthogonal Matrices

D and E are orthogonal

```{r}
A %*% t(A)
B %*% t(B)
C %*% t(C)
D %*% t(D) 
E %*% t(E) 
```

Creation of List

```{r}


```

When rows are appended in R they are added row by row.
When preallocated space is reserved beforehand.
Preallocating is better because it does not require memory to be allocated repeatedly.

Appending to Vectors

```{r}
v <- c(1,2)
v <- c(v,3)
```

Preallocating Vectors

```{r}
v <- vector("list",3)

```

Appending to Dataframe

```{r}
suburbs <- data.frame(city="Chicago",county="Cook",state="IL",pop=2853114)
newRow <- data.frame(city="West Dundee", county="Kane", state="IL", pop=5428)
suburbs <- rbind(suburbs, newRow)

```

Preallocating to Dataframe

```{r}
suburbs <- data.frame(city=character(2),pop=numeric(2))

```

Appending to List

```{r}
resultsa <- list(1,2,3,4,5)
resultsb <- list(6,7,8,9,10)
outlist <- list(resultsa)
outlist <- append(outlist, list(resultsb))
```

Preallocating to List
Use similar method to preallocating vectors


Loading Boston dataset of MASS package

```{r}
library("MASS")
data(Boston)
newdf <- data.frame(Boston[1], Boston[6])
colnames(newdf) <- c('Crime Rate','Room Occupancy')
newdf
```

