---
title: "Week5 R Assignment"
output: html_document
---

When rows are appended in R they are added row by row.
When preallocated space is reserved beforehand.
Preallocating is better because it does not require memory to be allocated repeatedly.

Appending to Vectors

```{r}
v <- c(1,2)
v <- c(v,3)
```

Preallocating Vectors

```{r}
v <- vector("list",3)

```

Appending to Dataframe

```{r}
suburbs <- data.frame(city="Chicago",county="Cook",state="IL",pop=2853114)
newRow <- data.frame(city="West Dundee", county="Kane", state="IL", pop=5428)
suburbs <- rbind(suburbs, newRow)

```

Preallocating to Dataframe

```{r}
suburbs <- data.frame(city=character(2),pop=numeric(2))

```

Appending to List

```{r}
resultsa <- list(1,2,3,4,5)
resultsb <- list(6,7,8,9,10)
outlist <- list(resultsa)
outlist <- append(outlist, list(resultsb))
```

Preallocating to List
Use similar method to preallocating vectors


Loading Boston dataset of MASS package

```{r}
library("MASS")
data(Boston)
newdf <- data.frame(Boston[1], Boston[6])
colnames(newdf) <- c('Crime Rate','Room Occupancy')
newdf
```

